### 2011-04-14 Spatial_adaptation/local-adaptation.tex
/* Local Adaptation */ more notes

>>>>

Note that if $\tau$ is the first time that the new patch $A$ is occupied,
and $Z_t$ is the state of the proces, then
\[
    \partial_t \P\{ \tau > t \} = \int \int_A s(x) \kappa(y-x) \E[ Z_t(dx) | \tau > t ] dy \P\{ \tau > t \}
\]
... so we want to find the first integral (and show that for $t>\epsilon$ it is approximately constant).
Since we are also taking the small-dispersal limit, this seems tricky.

Another option: we are trying to find the first time that a mutant appears in patch $A$ {\em and fixes locally};
if the benefit is small then there may be many unsuccessful migrants first.
Suppose we modify the process so that offspring appearing in $A$ have distribution {\em conditioned on local extinction};
then we suppose that each such individual has probability ${}\approx 2s_b$ of fixation,
so that the mean number of such offspring per generation times $2s_b$ gives us the rate we are looking for.
A supercritical branching process conditioned on extinction is a subcritical branching process,
with mean offspring number $\partial_z \E[z^N]\vert_{z=p}$, where $N$ is the offspring number and $p$ is the probability of extinction.
In the case of a binomial (check this?) branching, this changes $s$ to $-s$.
